\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.
\usepackage{multirow}
\usepackage{psfrag}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{array}
\usepackage{forloop}
\input{macros}

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{A Sparse Linear Model for Saliency-Guided Decolorization}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   Unlike most of the existing decolorization techniques that emphasize
   preserving image features revealed in the input color space,
   our proposed method focuses on exploring those in a higher dimensional
   feature space. The shift of paradigm is motivated by that decolorization
   is often sensitive to adopting the various color systems. 
   The results of converting the same color image expressed in 
   different color spaces could vary significantly. We instead consider
   constructing an image-dependent feature space by learning a representative
   dictionary, and carry out decolorizing an image by retaining the structures
   there. To this end, for a given image, the atoms of the dictionary 
   are systematically collected to reflect the visually important/salient contents,
   and also to concisely reduce chromatic redundancy. 
   A sparse linear model with respect to the learned dictionary is then assumed.
   Finally, a linear projection from the feature space of higher dimension
   to grayscale can be optimized to accomplish the conversion.
   Experimental results and comparisons with the state-of-the-art are provided
   to illustrate the various advantages of the proposed framework to decolorization.
\end{abstract}

%%%%%%%%% BODY TEXT
\input{introduction}
\input{related_work}
\input{method}
\input{experiments}
\input{results}

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}
